\documentclass[11pt]{article}

\usepackage{xcolor}
\definecolor{azureblue}{RGB}{0,120,215}

\usepackage[hidelinks,colorlinks=true,linkcolor=azureblue,urlcolor=azureblue]{hyperref}
\usepackage[margin=0.85in]{geometry}
\usepackage{charter}
\usepackage{parskip}
\setlength{\parskip}{8pt}

\begin{document}

\begin{flushleft}
\textbf{\Large Aditya Sugandhi} \hfill \today\\
Tallahassee, FL \textbar\ +1 4485006857 \textbar\ \href{mailto:adityasugandhi.work@outlook.com}{adityasugandhi.work@outlook.com} \textbar\ \href{https://github.com/adityasugandhi}{GitHub}
\end{flushleft}

\vspace{-5pt}

\textbf{GE Vernova -- Advanced Research Division}\\
\textbf{RE: AI Agent Engineer (R5021726)}

Dear Hiring Manager,

I am excited to apply for the AI Agent Engineer position at GE Vernova. With a Master's in Computer Science and hands-on experience building \textbf{production multi-agent systems with MCP protocol, LangGraph, and RAG pipelines}, I can contribute meaningfully to your autonomous AI initiatives for energy transition.

\textbf{MCP Protocol Expertise:} At Florida State University, I architected an \textbf{AI-powered ecosystem using Claude Code with 10+ MCP servers}. I built 3 custom MCP servers for Oracle database operations and BACnet device management, improving workflow efficiency by \textbf{60\% across 15+ engineering teams}. This hands-on experience with agent orchestration protocols---specifically mentioned in your requirements---positions me uniquely for your team.

\textbf{Multi-Agent System Development:} I've built production-grade multi-agent systems including: a \textbf{21-node LangGraph workflow} for B2B sales automation with RAG and conditional routing; a \textbf{3-agent executive intelligence dashboard} using NVIDIA Nemotron models with 13 function-calling tools; and asynchronous microservices processing \textbf{35k+ devices with 99.2\% accuracy}.

\textbf{Energy Sector Relevance:} My current role involves \textbf{building automation systems (BACnet/IP)}, directly related to energy management infrastructure. I understand the intersection of AI agents and physical systems---critical for GE Vernova's energy transition mission.

\textbf{Production ML \& NLP:} As an ML Researcher at FSU, I architected pipelines over 1TB+ datasets with LLMs, vector embeddings, and semantic search using Transformers and vector databases (ChromaDB, Qdrant).

I am drawn to GE Vernova's focus on autonomous AI agents for real-world energy challenges. I am authorized to work in the United States and open to relocation to Niskayuna, NY.

Thank you for considering my application. I look forward to discussing how my MCP and multi-agent experience can contribute to your Advanced Research team.

\vspace{5pt}
Sincerely,\\
\textbf{Aditya Sugandhi}

\end{document}
